A Test of the Frequency Independence Assumption of the System Parameters used in Geomagnetically Induced Current Calculations

### 2019-01-14 paper.tex
Updates from ShareLaTeX

%Text here ===>>>

%%

%  Numbered lines in equations:
%  To add line numbers to lines in equations,
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}

%\appendix
%\section{Here is a sample appendix}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_TF_aves_aobo_histograms-none-none-rectangular-parzen-ols_on_Z.pdf}
\caption{}
\label{histogram}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_TF_aves_GE_H-none-none-rectangular-parzen-ols_on_Z.pdf}
\caption{}
\label{H}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_TF_aves_GE_Z-none-none-rectangular-parzen-ols_on_Z.pdf}
\caption{}
\label{Z}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_TF_aves_GE_Phi-none-none-rectangular-parzen-ols_on_Z.pdf}
\caption{}
\label{Phi}
\end{figure}
